Articles of Association of London Hackspace Ltd.

### 2011-07-26 constitution/articles-body.tex
Add "Disputes" clause as per new GD1

>>>>

\section{Disputes}

\item
    If a dispute arises between members of the company about the validity
    or propriety of anything done by the members of the company under these
    articles, and the dispute cannot be resolved by agreement, the parties
    to the dispute must first try in good faith to settle the dispute by
    mediation before resorting to litigation.
